---
title: "ms_4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(janitor)  
library(gt)
library(dplyr)
library(rvest)
```

Below is the data I have scraped from my sources. The first dataset I retrieved 
is from WBEZ Chicago, which comprises data including school closings, openings, 
and the number of students who were displaced from 2002 to 2018. From this, I 
was able to extract two tables which I regard to be very relevant, one being 
a table listing all the schools which have closed throughout the years, and 
then a table of the number of impacted students at the various high schools. I
then found another data set from Chicago Tribune which lists every single 
school that faced budget cuts, as well as how much their budget increased or 
was slashed. I'll either try to find some way to indicate this on the map I am
conjuring in my mind currently, or perhaps construct an additional graph. 

I've also found a research report by the name of "When Schools Close: Effects 
on Displaced Students in Chicago Public Schools." This research report contains
numerous graphs and charts, with data such as tables of school closings and
the reasons for doing so (e.g. poor academics, underutilization). I think this
is enlightening new data I could use to color my maps even further. This is 
in a PDF format, so I'm wondering how best to scrape the data. I may have
to recreate the data in a table and use it then, as to the extent of my
knowledge I cannot scrape it since data isn't on a webpage. At the moment,
I am still considering an animated map, but with so much data I am trying
to configure how I will portray all the information. I am currently thinking of
having two to three additional graphs, but I do want an animated map that would
give a clear picture, as there is a very obfuscated understanding of the issue
currently within the CPS system.

Here are the links to my sources:

https://interactive.wbez.org/generation-school-closings/

https://docs.google.com/spreadsheets/u/1/d/e/2PACX-1vRmKox-lDNqhtUNL4WLl8x6DljIi3b0k1pYEmD7adfCwX-rGYyFw0XIjxNWkOfL6og3CHfUEHPMwv6k/pubhtml?urp=gmail_link#

https://www.chicagotribune.com/news/ct-2016-cps-school-budget-cuts-table-htmlstory.html

https://files.eric.ed.gov/fulltext/ED510792.pdf


```{r}
funds <- read_html("https://www.chicagotribune.com/news/ct-2016-cps-school-budget-cuts-table-htmlstory.html")
tab <- funds %>% 
  html_nodes("table")
tab <- tab[1] %>% 
  html_table 

shakeups <- read_html("https://docs.google.com/spreadsheets/u/1/d/e/2PACX-1vRmKox-lDNqhtUNL4WLl8x6DljIi3b0k1pYEmD7adfCwX-rGYyFw0XIjxNWkOfL6og3CHfUEHPMwv6k/pubhtml?urp=gmail_link#")
close <- shakeups %>% 
  html_nodes("table")
close <- close[1] %>% 
  html_table 

students <- shakeups %>% 
  html_nodes("table")
students <- students[3] %>% 
  html_table
```

